Combinatorial interpretations of holonomic recurrences

### 2021-09-04 article/main.tex
Unify bibliography

@@

The initial inspiration for the thesis came from the publication \textit{A natural counting of lambda terms}~\cite{zigzag}, which shows bijections among seemingly different tree structures, which are lambda trees, black-white trees\todo{cite} and zigzag free trees\todo{cite}. They share the same holonomic recurrence, but there is no known immediate connection between the holonomic recurrence and the structures itself.

@@

\begin{thebibliography}{9}
    \bibitem{zigzag}
    Maciej Bendkowski, Katarzyna Grygiel, Pierre Lescanne, Marek Zaionc,
    \textit{A natural counting of lambda terms},
    2016

    \bibitem{gfun}
    Bruno Salvy, Paul Zimmermann,
    \textit{GFUN : a maple package for the manipulation of generating and holonomic functions in one variable},
    [Research Report] RT-0143, INRIA. 1992, pp.14. ffinria-00070025f

    \bibitem{holotoolkit}
    Manuel Kauers,
    \textit{The Holonomic Toolkit},
    in: Carsten Schneider, Johannes Blümlein (eds) Computer Algebra in Quantum Field Theory. Texts \& Monographs in Symbolic Computation (A Series of the Research Institute for Symbolic Computation, Johannes Kepler University, Linz, Austria),
    Springer, Vienna,
    2013

    \bibitem{nonholo}
    Stefan Gerhold,
    \textit{Combinatorial sequences: Non-holonomicity and inequalities. Ph.D. thesis},
    RISC-Linz, Johannes Kepler Universitat Linz,
    2005

    \bibitem{complexity}
    Igor Pak,
    \textit{Complexity problems in enumerative combinatorics},
    2018

    \bibitem{binary}
    Jean-Luc Rémy,
    \textit{Un procédé itératif de dénombrement d’arbres binaires et son application à leur génération aléatoire}
    Informatique théorique, tome 19, no 2, 
    1985,
    p. 179-195

    \bibitem{motzkin}
    Serge Dulucq, Jean-Guy Penaud,
    \textit{Interprétation bijective d'une récurrence des nombres de Motzkin},
    Discrete Mathematics,
    Volume 256, Issue 3,
    2002,
    p. 671-676

    \bibitem{schroder}
    Dominique Foata, Doron Zeilberger,
    \textit{A Classic Proof of a Recurrence for a Very Classical Sequence}
    J. Comb., Ser. A, 80,
    1997, 380-384

    \bibitem{doron}
    Doron Zeilberger,
    \textit{e-mail conversation},
    2020

    % Non-cited

    \bibitem{remy}
    Laurent Alonso Alonso, Jean-Luc Rémy, and René Schott,
    \textit{A Linear-Time Algorithm for the Generation of Trees},
    Algorithmica 17,
    1997,
    p. 162-182

    \bibitem{note}
    Jarmo Siltaneva, Erkki Mäkinen,
    \textit{A Note on Rémy's Algorithm for Generating Random Binary Trees},
    Missouri Journal of Mathematical Sciences. 15. 103-109. 10.35834/2003/1502103,
    2003

    \bibitem{bodini}
    Axel Bacher, Olivier Bodini, Alice Jacquot,
    Efficient random sampling of binary and unary-binary trees via holonomic equations,
    2014

    % Additional

    \bibitem{transformator}
    Bartłomiej Puget,
    \textit{Transformator framework},
    \url{https://github.com/Larhard/transformator},
    2021

\end{thebibliography}

>>>>

\RequirePackage[maxbibnames=99]{biblatex}
\addbibresource{bibliography.bib}

@@

The initial inspiration for the thesis came from the publication \textit{A natural counting of lambda terms}~\cite{inspiration}, which shows bijections among seemingly different tree structures, which are lambda trees, black-white trees~\cite{blackwhite} and zigzag free trees\todo{cite}. They share the same holonomic recurrence, but there is no known immediate connection between the holonomic recurrence and the structures itself.

@@

\printbibliography
